### 2017-06-01 04-experimental-setup.tex

To evaluate our implementations, we use publicly available
community networks from the SNAP collection~\cite{snapnets}.
Table~\ref{table-snap}
outlines the graph properties of the networks used.

>>>>

To evaluate our implementations, we use publicly available
community networks from the Stanford Network Analysis Project (SNAP)
collection~\cite{snapnets}, including the largest networks.
Table~\ref{table-snap}
outlines the graph properties of the networks used.
